Automated Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{NSF Grant ???} }

### 2021-03-31 paper/paper_new.tex
Fixed formatting in author list.
Added states in addresses.

\author{
\IEEEauthorblockN{Joel Pepper}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Drexel University}\\
Philadelphia, USA\\
0000-0002-1601-8729}
\and
\IEEEauthorblockN{Jane Greenberg}
\IEEEauthorblockA{\textit{Department of Information Science} \\
\textit{Drexel University}\\
Philadelphia, USA\\
0000-0001-7819-5360}
\and
\IEEEauthorblockN{Yasin Baki\c{s}}
\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
\textit{Tulane University}\\
New Orleans, USA\\
0000-0001-6144-9440}
\and
\IEEEauthorblockN{Xiaojun Wang}
\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
\textit{Tulane University}\\
New Orleans, USA\\
0000-0001-8639-6795}
\and
\IEEEauthorblockN{Henry Bart Jr.}
\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
\textit{Tulane University}\\
New Orleans, USA\\
0000-0002-5662-9444}
\and
\IEEEauthorblockN{David Breen}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Drexel University}\\
Philadelphia, USA\\
0000-0002-1376-5008}
}

>>>>

\author{
\IEEEauthorblockN{Joel Pepper}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Drexel University}\\
Philadelphia, PA\hspace{3mm}USA\\
0000-0002-1601-8729}\\
\IEEEauthorblockN{Xiaojun Wang}
\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
\textit{Tulane University}\\
New Orleans, LA\hspace{3mm}USA\\
0000-0001-8639-6795}
\and
\IEEEauthorblockN{Jane Greenberg}
\IEEEauthorblockA{\textit{Department of Information Science} \\
\textit{Drexel University}\\
Philadelphia, PA\hspace{3mm}USA\\
0000-0001-7819-5360}\\
\IEEEauthorblockN{Henry Bart Jr.}
\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
\textit{Tulane University}\\
New Orleans, LA\hspace{3mm}USA\\
0000-0002-5662-9444}
\and
\IEEEauthorblockN{Yasin Baki\c{s}}
\IEEEauthorblockA{\textit{Biodiversity Research Institute} \\
\textit{Tulane University}\\
New Orleans, LA\hspace{3mm}USA\\
0000-0001-6144-9440}\\
\IEEEauthorblockN{David Breen}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Drexel University}\\
Philadelphia, PA\hspace{3mm}USA\\
0000-0002-1376-5008}
}
